Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2018-02-08 paper-ieee-trans.tex
good layout of images
minor fix

\subsubsection{Continuous Integration (CI)}
\label{subsec:ci}
The {\sl INDIGO--DataCloud} project promoted the application of a CI scenario that enforces,
for any piece of software produced, the testing requirements defined in the SQA criteria,
as described in Section \ref{subsec:sqa}. Such environment requires an automation
ready--to--go infrastructure where the different services and technologies involved interact with each
other to trigger the source code validation pipeline for each candidate change. The
pipeline is mainly comprised by the code style validation, unit and functional testing
coverage. The CI pipeline is complemented with additional quality checks, such as 
integration tests for the software components where automation of this type of testing
is applicable, or security linters for the code static analysis of suspicious
constructs that could lead to security risks. Metrics gathering also takes part of
the CI pipeline so to have a per-change trend evolution of the common source code 
related metrics, such as the source lines of code (SLOC) or the cyclomatic complexity.

>>>>

\subsubsection{Continuous Integration (CI)}
\label{subsec:ci}
The {\sl INDIGO--DataCloud} project promoted the application of a CI scenario that enforces,
for any piece of software produced, the testing requirements defined in the SQA criteria,
as described in Section \ref{subsec:sqa}. Such environment requires an automation
ready--to--go infrastructure where the different services and technologies involved interact with each
other to trigger the source code validation pipeline for each candidate change. The
pipeline is mainly comprised by the code style validation, unit and functional testing
coverage. The CI pipeline is complemented with additional quality checks, such as 
integration tests for the software components where automation of this type of testing
is applicable, or security linters for the code static analysis of suspicious
constructs that could lead to security risks. Metrics gathering also takes part of
the CI pipeline so to have a per-change trend evolution of the common source code 
related metrics, such as SLOC or the cyclomatic complexity.
